---
title: "Diet and the human gut resistome: reproducible quantitative direction-of-evidence synthesis"
author: "Flores Ventura, Eduard"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    theme: readable
params:
  workbook: "../data/diet_ARG_quantitative_synthesis_extraction.xlsx"
  output_dir: "../outputs/generated"
  dpi_export: 1000
  install_missing_packages: true
---

```{r setup, include=FALSE}
# =============================================================================
# REPOSITORY-READY ARTICLE QUANTITATIVE SYNTHESIS PIPELINE
# =============================================================================
# Purpose
# -------
# This R Markdown file generates the article-ready quantitative synthesis inputs
# for the systematic review on diet, microbiome, and antimicrobial resistance genes
# (ARGs). It is intentionally designed for heterogeneous evidence where a single
# pooled random-effects meta-analysis would be misleading.
#
# Main logic
# ----------
# 1. Use a study-level direction-of-evidence synthesis as the primary quantitative
#    result: one prespecified judgement per study per domain.
# 2. Quantify uncertainty using Bayesian sign synthesis with a neutral Beta(1,1)
#    prior. Null/mixed evidence is retained as non-supportive in the conservative
#    display.
# 3. Use exact binomial sign tests only as a secondary check.
# 4. Treat outcome-level evidence as sensitivity only, because multiple rows from
#    the same study are statistically non-independent.
# 5. Display extractable effect sizes as quantitative anchors only; do not pool.
# 6. Export main and supplementary tables/figures as CSV, XLSX, PNG and TIFF.
# =============================================================================

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6.5,
  dpi = 320
)

required_packages <- c(
  "readxl", "dplyr", "tidyr", "stringr", "ggplot2", "forcats", "scales",
  "purrr", "tibble", "readr", "openxlsx", "knitr", "grid", "tools", "patchwork"
)

missing_packages <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_packages) > 0 && isTRUE(params$install_missing_packages)) {
  install.packages(missing_packages, repos = "https://cloud.r-project.org", type = "binary")
}

still_missing <- required_packages[!vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)]
if (length(still_missing) > 0) {
  stop("Missing packages: ", paste(still_missing, collapse = ", "),
       "\nInstall them manually or set params$install_missing_packages: true.")
}

invisible(lapply(required_packages, library, character.only = TRUE))

# ----------------------------- Paths ----------------------------------------
# Paths are written to work both in RStudio and from the command line.
# The default GitHub layout expects this Rmd in analysis/ and the workbook in data/.
input_dir <- tryCatch(dirname(normalizePath(knitr::current_input(), mustWork = FALSE)),
                      error = function(e) getwd())

is_absolute_path <- function(x) {
  grepl("^([A-Za-z]:|/|~)", x)
}

workbook_path <- params$workbook
if (!file.exists(workbook_path) && !is_absolute_path(workbook_path)) {
  local_candidate <- file.path(input_dir, workbook_path)
  if (file.exists(local_candidate)) workbook_path <- local_candidate
}
if (!file.exists(workbook_path)) {
  basename_candidate <- file.path(input_dir, basename(params$workbook))
  if (file.exists(basename_candidate)) workbook_path <- basename_candidate
}
if (!file.exists(workbook_path)) {
  stop("Workbook not found. Expected: ", params$workbook,
       "\nMove the XLSX to the repository data/ folder or edit params$workbook in the YAML header.")
}

out_dir <- params$output_dir
if (!is_absolute_path(out_dir)) {
  out_dir <- file.path(input_dir, out_dir)
}
table_dir <- file.path(out_dir, "tables")
figure_dir <- file.path(out_dir, "figures")
main_figure_dir <- file.path(figure_dir, "main_article")
supp_figure_dir <- file.path(figure_dir, "supplement")
text_dir <- file.path(out_dir, "manuscript_text")
for (d in c(out_dir, table_dir, figure_dir, main_figure_dir, supp_figure_dir, text_dir)) {
  dir.create(d, showWarnings = FALSE, recursive = TRUE)
}

DPI_EXPORT <- as.numeric(params$dpi_export)

# ----------------------------- Helpers --------------------------------------
clean_names <- function(x) {
  names(x) <- names(x) |>
    stringr::str_replace_all("[^A-Za-z0-9]+", "_") |>
    stringr::str_replace_all("^_+|_+$", "") |>
    stringr::str_to_lower()
  x
}

safe_read_sheet <- function(path, sheet, skip = 3) {
  if (!sheet %in% readxl::excel_sheets(path)) {
    stop("Sheet not found: ", sheet, " in ", path)
  }
  x <- readxl::read_excel(path, sheet = sheet, skip = skip)
  x <- clean_names(x)
  x <- x[rowSums(!is.na(x)) > 0, , drop = FALSE]
  x
}

as_yes <- function(x) {
  stringr::str_to_lower(stringr::str_trim(as.character(x))) %in% c("yes", "y", "true", "1")
}

as_num <- function(x) suppressWarnings(as.numeric(x))

write_csv_table <- function(x, filename) {
  readr::write_csv(x, file.path(table_dir, filename), na = "")
  invisible(x)
}

save_article_plot <- function(plot, name, width = 10, height = 6.5,
                              dpi = DPI_EXPORT, main = TRUE) {
  export_dir <- if (isTRUE(main)) main_figure_dir else supp_figure_dir
  png_path <- file.path(export_dir, paste0(name, ".png"))
  tiff_path <- file.path(export_dir, paste0(name, ".tiff"))
  pdf_path <- file.path(export_dir, paste0(name, ".pdf"))

  ggplot2::ggsave(png_path, plot = plot, width = width, height = height,
                  units = "in", dpi = dpi, bg = "white")
  ggplot2::ggsave(tiff_path, plot = plot, width = width, height = height,
                  units = "in", dpi = dpi, bg = "white", device = "tiff",
                  compression = "lzw")
  ggplot2::ggsave(pdf_path, plot = plot, width = width, height = height,
                  units = "in", bg = "white")

  tibble::tibble(
    figure = name,
    set = ifelse(main, "Main article", "Supplement"),
    png = png_path,
    tiff = tiff_path,
    pdf = pdf_path,
    dpi = dpi,
    width_in = width,
    height_in = height
  )
}

format_p <- function(p) {
  dplyr::case_when(
    is.na(p) ~ NA_character_,
    p < 0.001 ~ "<0.001",
    TRUE ~ sprintf("%.3f", p)
  )
}

fmt2 <- function(x) ifelse(is.na(x), NA_character_, sprintf("%.2f", x))
fmt3 <- function(x) ifelse(is.na(x), NA_character_, sprintf("%.3f", x))
short_wrap <- function(x, width = 30) stringr::str_wrap(as.character(x), width = width)

sign_test_p <- function(k, n, alternative = "greater") {
  if (is.na(k) || is.na(n) || n <= 0) return(NA_real_)
  stats::binom.test(k, n, p = 0.5, alternative = alternative)$p.value
}

clean_direction <- function(x) {
  dplyr::case_when(
    stringr::str_detect(stringr::str_to_lower(as.character(x)), "support") ~ "Supportive",
    stringr::str_detect(stringr::str_to_lower(as.character(x)), "opposite") ~ "Opposite",
    TRUE ~ "Null/mixed"
  )
}

classify_directness <- function(x) {
  x_low <- stringr::str_to_lower(as.character(x))
  dplyr::case_when(
    stringr::str_detect(x_low, "indirect") & stringr::str_detect(x_low, "mechan") ~ "Indirect/mechanistic",
    stringr::str_detect(x_low, "indirect") ~ "Indirect/mechanistic",
    stringr::str_detect(x_low, "mechan") ~ "Indirect/mechanistic",
    TRUE ~ "Direct/partly direct"
  )
}

make_directness_code <- function(x) {
  x_low <- stringr::str_to_lower(as.character(x))
  dplyr::case_when(
    stringr::str_detect(x_low, "direct and mechan") ~ "D+M",
    stringr::str_detect(x_low, "direct intervention") ~ "D-int",
    stringr::str_detect(x_low, "direct") ~ "D",
    stringr::str_detect(x_low, "indirect intervention") ~ "I-int",
    stringr::str_detect(x_low, "indirect") ~ "I",
    stringr::str_detect(x_low, "mechan") ~ "M",
    TRUE ~ "NR"
  )
}

# Safe labels for specific domain names.
standardize_domain <- function(x) {
  x <- as.character(x)
  dplyr::case_when(
    x == "Intervention / probiotic" ~ "Infant probiotic/synbiotic interventions",
    x == "Behaviour / diet" ~ "Adult behavioural/dietary patterns",
    TRUE ~ x
  )
}

domain_levels_main <- c(
  "Infant feeding",
  "Infant probiotic/synbiotic interventions",
  "Adult behavioural/dietary patterns",
  "Geography / urbanization"
)

# Primary manuscript panels requested for the article-ready Bayesian and harvest figures.
# Geography / urbanization is retained in the extraction tables and supplementary audit
# outputs, but removed from the main Bayesian direction-of-evidence figure.
domain_levels_primary <- c(
  "Infant feeding",
  "Infant probiotic/synbiotic interventions",
  "Adult behavioural/dietary patterns"
)

# Secondary descriptive combined synthesis across the three primary manuscript sections.
# This is useful for overall consistency but is not interpreted as a pooled effect size.
combined_domain_label <- "All domains combined"
domain_levels_bayesian <- c(domain_levels_primary, combined_domain_label)

# Exact Results-section titles from the manuscript. These are used as panel titles.
manuscript_section_titles <- c(
  "Infant feeding" = "Breastfeeding, formula feeding and infant ARG dynamics",
  "Infant probiotic/synbiotic interventions" = "Dietary interventions and probiotic/synbiotic modulation of ARGs",
  "Adult behavioural/dietary patterns" = "Dietary behavioural patterns",
  "All domains combined" = "All domains combined",
  "Geography / urbanization" = "Dietary-associated geographical patterns"
)

manuscript_section_title <- function(x) {
  x_chr <- as.character(x)
  out <- manuscript_section_titles[x_chr]
  out[is.na(out)] <- x_chr[is.na(out)]
  unname(out)
}

section_cols <- c(
  "Infant feeding" = "#2C7FB8",
  "Infant probiotic/synbiotic interventions" = "#31A354",
  "Adult behavioural/dietary patterns" = "#F16913",
  "All domains combined" = "#4D4D4D",
  "Geography / urbanization" = "#756BB1"
)

main_section_labels <- paste0(LETTERS[seq_along(domain_levels_primary)], ") ", manuscript_section_titles[domain_levels_primary])

# Domains with only one eligible study are not treated as synthesis domains.
# They can be described narratively or retained in the extraction workbook, but they
# are excluded from primary quantitative synthesis figures/tables because n = 1
# cannot support a domain-level consistency estimate.
excluded_synthesis_domains <- c("Intervention / diet")

# Journal-safe colors. Change here only if needed.
direction_cols <- c(
  "Supportive" = "#18B7B7",
  "Null/mixed" = "#F8766D",
  "Opposite" = "#7A1F1F"
)
node_cols <- c(
  "Exposure" = "#31C75B",
  "Microbiome mediator" = "#69A7F2",
  "ARG outcome" = "#F27A73"
)
traffic_cols <- c(
  "Ready" = "#1B9E77",
  "Not ready" = "#D95F02",
  "Future only" = "#7570B3"
)

article_theme <- ggplot2::theme_minimal(base_size = 12) +
  ggplot2::theme(
    plot.title = ggplot2::element_text(face = "bold", size = 15, margin = ggplot2::margin(b = 4)),
    plot.subtitle = ggplot2::element_text(size = 11, color = "grey30", margin = ggplot2::margin(b = 8)),
    axis.title = ggplot2::element_text(face = "bold"),
    legend.position = "bottom",
    panel.grid.minor = ggplot2::element_blank(),
    strip.text = ggplot2::element_text(face = "bold", size = 10),
    plot.margin = ggplot2::margin(10, 16, 10, 16)
  )
```

# 1. Aim and final synthesis strategy

This pipeline produces the final article inputs for a **quantified SWiM-compatible synthesis** of diet, microbiome and ARG evidence. It does **not** force a pooled random-effects meta-analysis when the available effect sizes are not exchangeable.

The recommended article structure is:

1. **Main Table:** study-level direction-of-evidence synthesis with Bayesian posterior estimates for the three primary manuscript sections plus a secondary descriptive all-domains combined analysis.
2. **Main Figure:** Bayesian posterior probability of supportive evidence for the three primary manuscript sections and the secondary combined analysis, ordered as they appear in the manuscript.
3. **Main Figure:** cleaned pathway-based synthesis map.
4. **Main Figure / article panel:** combined A4-ready harvest plot plus Bayesian direction-of-evidence panel, exported as PNG/PDF/TIFF at 1000 dpi.
5. **Supplement:** full-domain audit tables, meta-analysis readiness, descriptive effect-size anchors, outcome-level sensitivity and risk-of-bias/directness sensitivity.

The previous "Intervention / diet" domain is intentionally excluded from the primary synthesis because it contains only one study. "Geography / urbanization" is retained in extraction and supplementary audit outputs but is removed from the main Bayesian direction-of-evidence figure as requested.

# 2. Load extraction workbook

```{r load-data}
study_master <- safe_read_sheet(workbook_path, "Study_Master")
infant <- safe_read_sheet(workbook_path, "Infant_Feeding")
interventions <- safe_read_sheet(workbook_path, "Probiotic_Interventions")
behaviour <- safe_read_sheet(workbook_path, "Behaviour_Diet")
geography <- safe_read_sheet(workbook_path, "Geography_Urbanization")
outcomes <- safe_read_sheet(workbook_path, "Outcome_Level_Evidence")
effects <- safe_read_sheet(workbook_path, "Effect_Size_Candidates")
pathways <- safe_read_sheet(workbook_path, "Pathway_Evidence")
rob <- safe_read_sheet(workbook_path, "RoB_Directness")

study_master <- study_master |>
  dplyr::mutate(
    analysis_domain_original = analysis_domain,
    analysis_domain = standardize_domain(analysis_domain),
    analysis_domain = factor(analysis_domain, levels = unique(c(domain_levels_main, analysis_domain))),
    sample_size = as_num(sample_size),
    supportive_binary = as_num(supportive_binary),
    meta_ready_bool = as_yes(meta_ready),
    extractable_effect_size_bool = as_yes(extractable_effect_size),
    direction_clean = clean_direction(direction_study_level),
    directness_group = classify_directness(directness),
    directness_code = make_directness_code(directness)
  )

outcomes <- outcomes |>
  dplyr::mutate(
    analysis_domain = standardize_domain(analysis_domain),
    analysis_domain = factor(analysis_domain, levels = unique(c(domain_levels_main, analysis_domain))),
    supportive_binary = as_num(supportive_binary),
    include_primary_study_level = as_num(include_primary_study_level),
    include_outcome_sensitivity = as_num(include_outcome_sensitivity),
    direction_clean = clean_direction(direction)
  )

effects <- effects |>
  dplyr::mutate(
    analysis_domain = standardize_domain(analysis_domain),
    analysis_domain = factor(analysis_domain, levels = unique(c(domain_levels_main, analysis_domain))),
    log_effect = as_num(log_effect),
    se_log_effect = as_num(se_log_effect),
    ci_lower = as_num(ci_lower),
    ci_upper = as_num(ci_upper),
    effect_value = as_num(effect_value),
    events_exposed = as_num(events_exposed),
    non_events_exposed = as_num(non_events_exposed),
    events_reference = as_num(events_reference),
    non_events_reference = as_num(non_events_reference),
    n_exposed = as_num(n_exposed),
    n_reference = as_num(n_reference),
    n_total = as_num(n_total),
    meta_ready_bool = as_yes(meta_ready),
    has_uncertainty = !is.na(se_log_effect) & se_log_effect > 0
  )

pathways <- pathways |>
  dplyr::mutate(
    analysis_domain = standardize_domain(analysis_domain),
    analysis_domain = factor(analysis_domain, levels = unique(c(domain_levels_main, analysis_domain)))
  )

rob <- rob |>
  dplyr::mutate(use_in_primary_bool = as_yes(use_in_primary))

# Exclude n = 1 domains from the quantitative synthesis objects.
# This avoids presenting a single study as a domain-level Bayesian/posterior synthesis.
single_study_or_narrative_domains <- study_master |>
  dplyr::filter(as.character(analysis_domain) %in% excluded_synthesis_domains)

study_master <- study_master |>
  dplyr::filter(!as.character(analysis_domain) %in% excluded_synthesis_domains)

outcomes <- outcomes |>
  dplyr::filter(!as.character(analysis_domain) %in% excluded_synthesis_domains)

effects <- effects |>
  dplyr::filter(!as.character(analysis_domain) %in% excluded_synthesis_domains)

pathways <- pathways |>
  dplyr::filter(!as.character(analysis_domain) %in% excluded_synthesis_domains)

cat("Workbook loaded from:\n", workbook_path, "\n\n")
cat("Outputs will be written to:\n", out_dir, "\n")
```

# 3. Study-level extraction summary

```{r table-study-extraction}
study_table <- study_master |>
  dplyr::select(
    study_id, first_author_year, year, analysis_domain, country_region,
    population_life_stage, sample_size, study_design, dietary_exposure_class,
    arg_outcomes, direction_study_level, directness, risk_of_bias_working,
    extractable_effect_size, meta_ready, source_document, source_location, notes
  ) |>
  dplyr::arrange(analysis_domain, first_author_year)

write_csv_table(study_table, "table_01_study_level_extraction_summary.csv")

knitr::kable(
  study_table |>
    dplyr::select(first_author_year, analysis_domain, country_region, population_life_stage,
                  sample_size, study_design, dietary_exposure_class, direction_study_level,
                  directness, meta_ready),
  caption = "Table 1. Study-level extraction summary for article input.",
  align = "l"
)
```

# 4. Meta-analysis readiness check

```{r meta-readiness}
meta_readiness <- effects |>
  dplyr::mutate(metric_outcome_key = paste(analysis_domain, effect_metric, outcome, sep = " | ")) |>
  dplyr::group_by(analysis_domain, effect_metric, outcome) |>
  dplyr::summarise(
    rows = dplyr::n(),
    unique_studies = dplyr::n_distinct(study_id),
    meta_ready_rows = sum(meta_ready_bool, na.rm = TRUE),
    rows_with_log_effect = sum(!is.na(log_effect)),
    rows_with_uncertainty = sum(has_uncertainty, na.rm = TRUE),
    candidate_for_random_effects = unique_studies >= 3 & meta_ready_rows >= 3 & rows_with_uncertainty >= 3,
    readiness = dplyr::case_when(
      candidate_for_random_effects ~ "Ready",
      unique_studies >= 2 & rows_with_log_effect >= 2 ~ "Future only",
      TRUE ~ "Not ready"
    ),
    reason = dplyr::case_when(
      candidate_for_random_effects ~ "At least 3 comparable estimates with uncertainty.",
      unique_studies >= 2 & rows_with_log_effect >= 2 ~ "Potential future subset if uncertainty/comparability improves.",
      TRUE ~ "Too few comparable estimates and/or missing uncertainty."
    ),
    .groups = "drop"
  ) |>
  dplyr::arrange(desc(candidate_for_random_effects), analysis_domain, effect_metric)

write_csv_table(meta_readiness, "table_02_meta_analysis_readiness_check.csv")

knitr::kable(
  meta_readiness,
  caption = "Table 2. Meta-analysis readiness check. A pooled random-effects model is only appropriate when at least three comparable estimates with uncertainty are available within the same domain, metric and outcome.",
  align = "l"
)

if (!any(meta_readiness$candidate_for_random_effects, na.rm = TRUE)) {
  cat("\n**Conclusion:** No random-effects meta-analysis is run as a main result. Extractable effects are quantitative anchors only.\n")
}
```

# 5. Primary study-level direction synthesis

```{r study-level-direction}
study_sign <- study_master |>
  dplyr::filter(!is.na(study_id), !is.na(direction_study_level)) |>
  dplyr::mutate(
    direction_clean = clean_direction(direction_study_level),
    sign_for_binomial = dplyr::case_when(
      direction_clean == "Supportive" ~ 1,
      direction_clean == "Opposite" ~ 0,
      TRUE ~ NA_real_
    )
  )

study_direction <- study_sign |>
  dplyr::group_by(analysis_domain) |>
  dplyr::summarise(
    studies = dplyr::n(),
    supportive = sum(direction_clean == "Supportive", na.rm = TRUE),
    null_mixed = sum(direction_clean == "Null/mixed", na.rm = TRUE),
    opposite = sum(direction_clean == "Opposite", na.rm = TRUE),
    directional_n = sum(!is.na(sign_for_binomial)),
    supportive_directional = sum(sign_for_binomial == 1, na.rm = TRUE),
    total_sample_size = sum(sample_size, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    supportive_prop_all = supportive / studies,
    supportive_prop_directional = dplyr::if_else(directional_n > 0, supportive_directional / directional_n, NA_real_),
    exact_binomial_p_one_sided = as.numeric(mapply(sign_test_p, supportive_directional, directional_n)),
    # Conservative Bayesian model: null/mixed is counted as non-supportive.
    posterior_alpha_all = 1 + supportive,
    posterior_beta_all = 1 + studies - supportive,
    posterior_mean_all = posterior_alpha_all / (posterior_alpha_all + posterior_beta_all),
    posterior_lcl_all = qbeta(0.025, posterior_alpha_all, posterior_beta_all),
    posterior_ucl_all = qbeta(0.975, posterior_alpha_all, posterior_beta_all),
    # Directional-only posterior: excludes null/mixed evidence, like the exact sign test.
    posterior_alpha_directional = 1 + supportive_directional,
    posterior_beta_directional = 1 + directional_n - supportive_directional,
    posterior_mean_directional = dplyr::if_else(directional_n > 0, posterior_alpha_directional / (posterior_alpha_directional + posterior_beta_directional), NA_real_),
    posterior_lcl_directional = dplyr::if_else(directional_n > 0, qbeta(0.025, posterior_alpha_directional, posterior_beta_directional), NA_real_),
    posterior_ucl_directional = dplyr::if_else(directional_n > 0, qbeta(0.975, posterior_alpha_directional, posterior_beta_directional), NA_real_)
  )

study_direction_all <- study_sign |>
  dplyr::filter(as.character(analysis_domain) %in% domain_levels_primary) |>
  dplyr::summarise(
    analysis_domain = combined_domain_label,
    studies = dplyr::n(),
    supportive = sum(direction_clean == "Supportive", na.rm = TRUE),
    null_mixed = sum(direction_clean == "Null/mixed", na.rm = TRUE),
    opposite = sum(direction_clean == "Opposite", na.rm = TRUE),
    directional_n = sum(!is.na(sign_for_binomial)),
    supportive_directional = sum(sign_for_binomial == 1, na.rm = TRUE),
    total_sample_size = sum(sample_size, na.rm = TRUE)
  ) |>
  dplyr::mutate(
    supportive_prop_all = supportive / studies,
    supportive_prop_directional = supportive_directional / directional_n,
    exact_binomial_p_one_sided = sign_test_p(supportive_directional, directional_n),
    posterior_alpha_all = 1 + supportive,
    posterior_beta_all = 1 + studies - supportive,
    posterior_mean_all = posterior_alpha_all / (posterior_alpha_all + posterior_beta_all),
    posterior_lcl_all = qbeta(0.025, posterior_alpha_all, posterior_beta_all),
    posterior_ucl_all = qbeta(0.975, posterior_alpha_all, posterior_beta_all),
    posterior_alpha_directional = 1 + supportive_directional,
    posterior_beta_directional = 1 + directional_n - supportive_directional,
    posterior_mean_directional = posterior_alpha_directional / (posterior_alpha_directional + posterior_beta_directional),
    posterior_lcl_directional = qbeta(0.025, posterior_alpha_directional, posterior_beta_directional),
    posterior_ucl_directional = qbeta(0.975, posterior_alpha_directional, posterior_beta_directional)
  )

study_direction_final <- dplyr::bind_rows(study_direction, study_direction_all)

article_results <- study_direction_final |>
  dplyr::mutate(
    result_sentence = paste0(
      analysis_domain, ": ", supportive, "/", studies,
      " studies were supportive; ", null_mixed, " null/mixed and ", opposite,
      " opposite. Conservative Bayesian posterior mean for support = ",
      fmt2(posterior_mean_all), " (95% CrI ", fmt2(posterior_lcl_all), "–", fmt2(posterior_ucl_all), ")."
    )
  ) |>
  dplyr::select(analysis_domain, studies, supportive, null_mixed, opposite,
                exact_binomial_p_one_sided, posterior_mean_all, posterior_lcl_all,
                posterior_ucl_all, result_sentence)

write_csv_table(study_direction_final, "table_03_primary_study_level_direction_synthesis.csv")
write_csv_table(article_results, "table_08_article_ready_direction_results.csv")

combined_result_sentence <- article_results |>
  dplyr::filter(analysis_domain == combined_domain_label) |>
  dplyr::pull(result_sentence)

readr::write_lines(
  c(
    "Secondary all-domains combined interpretation:",
    combined_result_sentence,
    "",
    "Interpretation: this combined analysis summarizes evidence consistency across the three primary manuscript sections only. It is not a pooled effect-size estimate and should not be interpreted as the magnitude of diet-related effects on ARGs."
  ),
  file.path(text_dir, "secondary_all_domains_combined_interpretation.txt")
)

main_results_table <- study_direction_final |>
  dplyr::filter(as.character(analysis_domain) %in% domain_levels_bayesian) |>
  dplyr::mutate(
    analysis_domain = factor(as.character(analysis_domain), levels = domain_levels_bayesian),
    panel_letter = LETTERS[match(as.character(analysis_domain), domain_levels_bayesian)],
    `Manuscript section` = dplyr::if_else(
      as.character(analysis_domain) == combined_domain_label,
      paste0(panel_letter, ") All domains combined (descriptive)"),
      paste0(panel_letter, ") ", manuscript_section_title(analysis_domain))
    ),
    `Supportive / studies` = paste0(supportive, "/", studies),
    `Null/mixed` = null_mixed,
    `Opposite` = opposite,
    `Posterior mean support` = fmt2(posterior_mean_all),
    `95% CrI` = paste0(fmt2(posterior_lcl_all), "–", fmt2(posterior_ucl_all)),
    `Exact sign-test p` = format_p(exact_binomial_p_one_sided)
  ) |>
  dplyr::arrange(analysis_domain) |>
  dplyr::select(
    `Manuscript section`,
    `Supportive / studies`, `Null/mixed`, `Opposite`,
    `Posterior mean support`, `95% CrI`, `Exact sign-test p`
  )

full_domain_results_table <- study_direction_final |>
  dplyr::filter(as.character(analysis_domain) != combined_domain_label) |>
  dplyr::mutate(
    `Manuscript section` = manuscript_section_title(analysis_domain),
    `Supportive / studies` = paste0(supportive, "/", studies),
    `Posterior mean support` = fmt2(posterior_mean_all),
    `95% CrI` = paste0(fmt2(posterior_lcl_all), "–", fmt2(posterior_ucl_all)),
    `Exact sign-test p` = format_p(exact_binomial_p_one_sided)
  )

write_csv_table(main_results_table, "MAIN_TABLE_01_study_level_direction_bayesian_summary.csv")
write_csv_table(full_domain_results_table, "SUPP_TABLE_full_domain_direction_bayesian_summary_including_geography.csv")

knitr::kable(
  main_results_table,
  caption = "Main Table 1. Study-level direction-of-evidence synthesis for the three primary manuscript sections plus a secondary descriptive combined analysis. Posterior estimates are evidence-consistency measures, not biological effect sizes.",
  align = "l"
)
```

# 6. Outcome-level sensitivity analysis

```{r outcome-sensitivity}
outcome_sensitivity <- outcomes |>
  dplyr::filter(include_outcome_sensitivity == 1, !is.na(direction)) |>
  dplyr::mutate(
    direction_clean = clean_direction(direction),
    sign_for_binomial = dplyr::case_when(
      direction_clean == "Supportive" ~ 1,
      direction_clean == "Opposite" ~ 0,
      TRUE ~ NA_real_
    )
  ) |>
  dplyr::group_by(analysis_domain) |>
  dplyr::summarise(
    outcome_rows = dplyr::n(),
    studies = dplyr::n_distinct(study_id),
    supportive = sum(direction_clean == "Supportive", na.rm = TRUE),
    null_mixed = sum(direction_clean == "Null/mixed", na.rm = TRUE),
    opposite = sum(direction_clean == "Opposite", na.rm = TRUE),
    directional_n = sum(!is.na(sign_for_binomial)),
    supportive_directional = sum(sign_for_binomial == 1, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::mutate(
    supportive_prop_all = supportive / outcome_rows,
    exact_binomial_p_one_sided = as.numeric(mapply(sign_test_p, supportive_directional, directional_n)),
    caution = "Sensitivity only: outcome rows from the same study are non-independent."
  )

write_csv_table(outcome_sensitivity, "table_04_outcome_level_sensitivity_non_independent.csv")

knitr::kable(
  outcome_sensitivity |>
    dplyr::mutate(
      supportive_prop_all = round(supportive_prop_all, 3),
      exact_binomial_p_one_sided = format_p(exact_binomial_p_one_sided)
    ),
  caption = "Supplementary Table. Outcome-level sensitivity analysis. These rows are not independent and should not be used as the primary synthesis.",
  align = "l"
)
```

# 7. Risk-of-bias and directness sensitivity

```{r rob-directness}
rob_summary <- study_master |>
  dplyr::left_join(rob |> dplyr::select(study_id, use_in_primary_bool, recommended_sensitivity_flag), by = "study_id") |>
  dplyr::mutate(
    directness_group = classify_directness(directness),
    use_in_primary_bool = dplyr::if_else(is.na(use_in_primary_bool), TRUE, use_in_primary_bool)
  ) |>
  dplyr::group_by(analysis_domain, directness_group, risk_of_bias_working) |>
  dplyr::summarise(studies = dplyr::n(), .groups = "drop") |>
  dplyr::arrange(analysis_domain, directness_group)

primary_restricted <- study_master |>
  dplyr::left_join(rob |> dplyr::select(study_id, use_in_primary_bool), by = "study_id") |>
  dplyr::mutate(use_in_primary_bool = dplyr::if_else(is.na(use_in_primary_bool), TRUE, use_in_primary_bool)) |>
  dplyr::filter(use_in_primary_bool, !is.na(direction_study_level)) |>
  dplyr::mutate(direction_clean = clean_direction(direction_study_level)) |>
  dplyr::group_by(analysis_domain) |>
  dplyr::summarise(
    retained_studies = dplyr::n(),
    supportive = sum(direction_clean == "Supportive"),
    null_mixed = sum(direction_clean == "Null/mixed"),
    opposite = sum(direction_clean == "Opposite"),
    supportive_prop_retained = supportive / retained_studies,
    .groups = "drop"
  )

write_csv_table(rob_summary, "table_05_risk_of_bias_directness_summary.csv")
write_csv_table(primary_restricted, "table_06_primary_restricted_directness_sensitivity.csv")

knitr::kable(
  primary_restricted |> dplyr::mutate(supportive_prop_retained = round(supportive_prop_retained, 3)),
  caption = "Supplementary Table. Restricted sensitivity using rows marked for primary use in the RoB/directness sheet.",
  align = "l"
)
```

# 8. Descriptive effect-size candidates: quantitative anchors only

```{r effect-size-candidates}
effect_table <- effects |>
  dplyr::mutate(
    ci_log_lower = dplyr::if_else(has_uncertainty, log_effect - 1.96 * se_log_effect, NA_real_),
    ci_log_upper = dplyr::if_else(has_uncertainty, log_effect + 1.96 * se_log_effect, NA_real_),
    effect_exp = exp(log_effect),
    ci_exp_lower = exp(ci_log_lower),
    ci_exp_upper = exp(ci_log_upper),
    recommended_use = dplyr::case_when(
      meta_ready_bool & has_uncertainty ~ "Descriptive quantitative anchor; do not pool unless comparable studies are added.",
      !is.na(log_effect) & !has_uncertainty ~ "Direction/magnitude only; no uncertainty available.",
      TRUE ~ "Narrative only."
    )
  ) |>
  dplyr::arrange(analysis_domain, effect_id)

write_csv_table(effect_table, "table_07_effect_size_candidates_descriptive_only.csv")

knitr::kable(
  effect_table |>
    dplyr::select(effect_id, first_author_year, analysis_domain, effect_metric, higher_risk_exposure,
                  reference_exposure, outcome, log_effect, se_log_effect, effect_exp, ci_exp_lower,
                  ci_exp_upper, meta_ready, recommended_use) |>
    dplyr::mutate(dplyr::across(where(is.numeric), ~ round(.x, 3))),
  caption = "Supplementary Table. Extractable effect-size candidates. Displayed descriptively only; no pooled model is calculated.",
  align = "l"
)
```

# 9. Main and supplementary figures

## Main Figure 1. Bayesian posterior probability of supportive evidence

```{r main-figure-bayesian-posteriors, fig.height=4.8}
posterior_source <- study_direction_final |>
  dplyr::filter(as.character(analysis_domain) %in% domain_levels_bayesian) |>
  dplyr::mutate(
    analysis_domain = factor(as.character(analysis_domain), levels = domain_levels_bayesian),
    panel_letter = LETTERS[match(as.character(analysis_domain), domain_levels_bayesian)],
    manuscript_section = dplyr::if_else(
      as.character(analysis_domain) == combined_domain_label,
      "All domains combined\n(descriptive)",
      manuscript_section_title(analysis_domain)
    ),
    panel_label = paste0(
      panel_letter, ") ", stringr::str_wrap(manuscript_section, 34), "\n",
      "Mean = ", fmt2(posterior_mean_all),
      "; 95% CrI ", fmt2(posterior_lcl_all), "–", fmt2(posterior_ucl_all),
      "; ", supportive, "/", studies, " supportive"
    )
  ) |>
  dplyr::arrange(analysis_domain)

theta_grid <- seq(0.001, 0.999, length.out = 900)
posterior_density <- purrr::map_dfr(seq_len(nrow(posterior_source)), function(i) {
  row <- posterior_source[i, ]
  tibble::tibble(
    analysis_domain = as.character(row$analysis_domain),
    panel_label = row$panel_label,
    theta = theta_grid,
    density = dbeta(theta_grid, row$posterior_alpha_all, row$posterior_beta_all),
    posterior_mean = row$posterior_mean_all,
    posterior_lcl = row$posterior_lcl_all,
    posterior_ucl = row$posterior_ucl_all
  )
}) |>
  dplyr::mutate(
    analysis_domain = factor(analysis_domain, levels = domain_levels_bayesian),
    panel_label = factor(panel_label, levels = unique(posterior_source$panel_label))
  )

fig_bayes_main <- ggplot2::ggplot(posterior_density, ggplot2::aes(x = theta, y = density)) +
  ggplot2::geom_area(ggplot2::aes(fill = analysis_domain), alpha = 0.66) +
  ggplot2::geom_line(ggplot2::aes(color = analysis_domain), linewidth = 0.85) +
  ggplot2::geom_vline(xintercept = 0.5, linetype = "dotted", linewidth = 0.65, color = "grey25") +
  ggplot2::geom_vline(ggplot2::aes(xintercept = posterior_mean), linetype = "solid", linewidth = 0.80) +
  ggplot2::geom_vline(ggplot2::aes(xintercept = posterior_lcl), linetype = "dashed", linewidth = 0.55) +
  ggplot2::geom_vline(ggplot2::aes(xintercept = posterior_ucl), linetype = "dashed", linewidth = 0.55) +
  ggplot2::facet_wrap(~ panel_label, scales = "free_y", ncol = 2) +
  ggplot2::scale_fill_manual(values = section_cols, guide = "none") +
  ggplot2::scale_color_manual(values = section_cols, guide = "none") +
  ggplot2::scale_x_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1), breaks = seq(0, 1, 0.25)) +
  ggplot2::labs(
    title = "Bayesian direction-of-evidence synthesis across manuscript sections",
    x = "Posterior probability of supportive evidence",
    y = "Posterior density"
  ) +
  article_theme +
  ggplot2::theme(
    strip.text = ggplot2::element_text(face = "bold", size = 9.2, lineheight = 0.92),
    legend.position = "none"
  )

fig_bayes_main
fig_manifest_bayes_main <- save_article_plot(fig_bayes_main, "MAIN_FIGURE_01_bayesian_direction_posteriors_primary_sections_plus_combined", width = 8.27, height = 6.9, main = TRUE)
```

## Main Figure 2. Clean pathway-based evidence synthesis

```{r main-figure-pathway-map, fig.height=10}
# Clean, compact node text for article use. If users edit Pathway_Evidence, this updates automatically.
pathway_plot_data <- pathways |>
  dplyr::filter(as.character(analysis_domain) %in% domain_levels_primary) |>
  dplyr::mutate(
    domain_chr = as.character(analysis_domain),
    # Number rows within domains for spacing.
    within_domain = dplyr::row_number(),
    y_raw = dplyr::row_number()
  ) |>
  dplyr::arrange(analysis_domain, y_raw) |>
  dplyr::group_by(analysis_domain) |>
  dplyr::mutate(row_in_domain = dplyr::row_number()) |>
  dplyr::ungroup()

# Build y positions with extra gap between domains to avoid overlap.
domain_order <- unique(as.character(pathway_plot_data$analysis_domain))
gap <- 0.80
y_positions <- list()
current_y <- 0
for (dom in rev(domain_order)) {
  idx <- which(as.character(pathway_plot_data$analysis_domain) == dom)
  n_dom <- length(idx)
  y_positions[[dom]] <- current_y + seq_len(n_dom)
  current_y <- current_y + n_dom + gap
}
pathway_plot_data$y <- NA_real_
for (dom in names(y_positions)) {
  idx <- which(as.character(pathway_plot_data$analysis_domain) == dom)
  pathway_plot_data$y[idx] <- rev(y_positions[[dom]])
}

nodes <- dplyr::bind_rows(
  pathway_plot_data |> dplyr::transmute(pathway_id, analysis_domain, y, x = 1, label = short_wrap(exposure_node, 25), node_type = "Exposure"),
  pathway_plot_data |> dplyr::transmute(pathway_id, analysis_domain, y, x = 2, label = short_wrap(microbiome_mediator_node, 31), node_type = "Microbiome mediator"),
  pathway_plot_data |> dplyr::transmute(pathway_id, analysis_domain, y, x = 3, label = short_wrap(arg_outcome_node, 30), node_type = "ARG outcome")
)

segments <- dplyr::bind_rows(
  pathway_plot_data |> dplyr::transmute(pathway_id, analysis_domain, y, x = 1.22, xend = 1.78, yend = y, evidence_strength),
  pathway_plot_data |> dplyr::transmute(pathway_id, analysis_domain, y, x = 2.22, xend = 2.78, yend = y, evidence_strength)
)

domain_labels <- pathway_plot_data |>
  dplyr::group_by(analysis_domain) |>
  dplyr::summarise(y = max(y) + 0.42, .groups = "drop") |>
  dplyr::mutate(x = 2, label = manuscript_section_title(analysis_domain))

fig_pathway_main <- ggplot2::ggplot() +
  ggplot2::geom_segment(
    data = segments,
    ggplot2::aes(x = x, xend = xend, y = y, yend = y, linetype = evidence_strength),
    arrow = grid::arrow(length = grid::unit(0.10, "inches")),
    linewidth = 0.55,
    color = "grey35"
  ) +
  ggplot2::geom_label(
    data = nodes,
    ggplot2::aes(x = x, y = y, label = label, fill = node_type),
    size = 2.8,
    label.size = 0.23,
    alpha = 0.98,
    lineheight = 0.92
  ) +
  ggplot2::geom_text(
    data = domain_labels,
    ggplot2::aes(x = x, y = y, label = label),
    fontface = "bold",
    size = 3.8
  ) +
  ggplot2::scale_fill_manual(values = node_cols) +
  ggplot2::scale_linetype_manual(values = c("High" = "solid", "Moderate" = "dashed", "Low" = "dotted"), drop = FALSE) +
  ggplot2::scale_x_continuous(
    breaks = c(1, 2, 3),
    labels = c("Diet / exposure", "Microbiome mediator", "ARG outcome"),
    limits = c(0.58, 3.42),
    expand = c(0, 0)
  ) +
  ggplot2::scale_y_continuous(NULL, breaks = NULL, expand = ggplot2::expansion(mult = c(0.04, 0.08))) +
  ggplot2::labs(
    title = "Pathway-based evidence synthesis across manuscript sections",
    subtitle = "Evidence is summarized as exposure → microbiome/ecological mediator → ARG outcome for the three primary manuscript sections.",
    x = NULL,
    fill = "Node type",
    linetype = "Evidence strength"
  ) +
  article_theme +
  ggplot2::theme(panel.grid = ggplot2::element_blank())

fig_pathway_main
fig_manifest_pathway_main <- save_article_plot(fig_pathway_main, "MAIN_FIGURE_02_pathway_evidence_map_clean", width = 13, height = 10, main = TRUE)
```

## Optional Main / Supplement Figure. Evidence strength gradient

```{r figure-evidence-strength-gradient, fig.height=5.5}
strength_data <- study_direction |>
  dplyr::mutate(
    analysis_domain = forcats::fct_reorder(as.character(analysis_domain), posterior_mean_all),
    label = paste0(supportive, "/", studies, " supportive"),
    width = posterior_ucl_all - posterior_lcl_all
  )

fig_strength <- ggplot2::ggplot(strength_data, ggplot2::aes(y = analysis_domain, x = posterior_mean_all)) +
  ggplot2::geom_vline(xintercept = 0.5, linetype = "dotted", color = "grey40") +
  ggplot2::geom_errorbarh(ggplot2::aes(xmin = posterior_lcl_all, xmax = posterior_ucl_all), height = 0.18, linewidth = 0.75, color = "grey25") +
  ggplot2::geom_point(ggplot2::aes(size = studies), shape = 21, fill = "#18B7B7", color = "black", alpha = 0.92) +
  ggplot2::geom_text(ggplot2::aes(label = label), nudge_y = 0.22, size = 3.2) +
  ggplot2::scale_x_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, 1)) +
  ggplot2::scale_size_continuous(range = c(4, 10)) +
  ggplot2::labs(
    title = "Evidence-strength gradient by synthesis domain",
    subtitle = "Posterior means and 95% credible intervals from conservative Bayesian sign synthesis.",
    x = "Posterior probability of supportive evidence",
    y = NULL,
    size = "Studies"
  ) +
  article_theme

fig_strength
fig_manifest_strength <- save_article_plot(fig_strength, "SUPP_FIGURE_evidence_strength_gradient", width = 10, height = 5.8, main = FALSE)
```

## Supplement Figure. Study-level direction composition by domain

```{r supp-figure-direction-composition, fig.height=6}
fig1_data <- study_sign |>
  dplyr::count(analysis_domain, direction_clean) |>
  dplyr::group_by(analysis_domain) |>
  dplyr::mutate(prop = n / sum(n), label = paste0(n, " studies")) |>
  dplyr::ungroup()

fig_direction_comp <- ggplot2::ggplot(fig1_data, ggplot2::aes(x = forcats::fct_rev(analysis_domain), y = prop, fill = direction_clean)) +
  ggplot2::geom_col(width = 0.72, color = "white") +
  ggplot2::geom_text(ggplot2::aes(label = ifelse(n > 0, paste0(n, "/", ave(n, analysis_domain, FUN = sum)), "")),
                     position = ggplot2::position_stack(vjust = 0.5), size = 3.4) +
  ggplot2::coord_flip() +
  ggplot2::scale_fill_manual(values = direction_cols, drop = FALSE) +
  ggplot2::scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  ggplot2::labs(
    title = "Study-level direction of evidence by synthesis domain",
    subtitle = "One row per study per domain; null/mixed evidence is retained.",
    x = NULL,
    y = "Study-level evidence classification",
    fill = "Direction"
  ) +
  article_theme

fig_direction_comp
fig_manifest_direction_comp <- save_article_plot(fig_direction_comp, "SUPP_FIGURE_study_level_direction_by_domain", width = 10, height = 6, main = FALSE)
```

## Main Figure 3. Harvest plot of diet–microbiome–ARG evidence

```{r main-figure-harvest, fig.height=7.4}
# Interpretation text saved for direct copy/paste into the manuscript.
harvest_legend_interpretation <- paste(
  "Harvest plot interpretation: each point represents one study-level finding.",
  "The x-axis shows the same three manuscript-section categories used in the Bayesian direction-of-evidence synthesis: infant feeding, infant probiotic or synbiotic interventions, and dietary behavioural patterns.",
  "The y-axis shows the citation followed by the study sample size.",
  "Point fill indicates direction of evidence: turquoise = supportive of the prespecified hypothesis, salmon = null or mixed evidence, and dark red = opposite evidence.",
  "Point shape indicates evidence directness: circles = direct or partly direct diet/feeding/intervention-to-ARG evidence; squares = indirect or mechanistic evidence.",
  "Point size is proportional to sample size using square-root scaling and capped to prevent very large studies from dominating the visual display; sample size is intentionally not repeated in the legend.",
  "This plot summarizes consistency and directness of evidence; it is not a pooled effect-size meta-analysis."
)
readr::write_lines(harvest_legend_interpretation, file.path(text_dir, "harvest_plot_legend_interpretation.txt"))
cat(harvest_legend_interpretation, "\n")

harvest_data_main <- study_sign |>
  dplyr::filter(as.character(analysis_domain) %in% domain_levels_primary) |>
  dplyr::mutate(
    analysis_domain = factor(as.character(analysis_domain), levels = domain_levels_primary),
    panel_letter = LETTERS[match(as.character(analysis_domain), domain_levels_primary)],
    manuscript_section = manuscript_section_title(analysis_domain),
    manuscript_section_panel = paste0(panel_letter, ") ", manuscript_section),
    manuscript_section_panel = factor(
      manuscript_section_panel,
      levels = paste0(LETTERS[seq_along(domain_levels_primary)], ") ", manuscript_section_titles[domain_levels_primary])
    ),
    manuscript_section_axis = stringr::str_wrap(as.character(manuscript_section_panel), width = 30),
    manuscript_section_axis = factor(
      manuscript_section_axis,
      levels = stringr::str_wrap(paste0(LETTERS[seq_along(domain_levels_primary)], ") ", manuscript_section_titles[domain_levels_primary]), width = 30)
    ),
    sample_size_plot = dplyr::if_else(is.na(sample_size) | sample_size <= 0, 25, pmin(sample_size, 650)),
    sample_size_sqrt = sqrt(sample_size_plot),
    directness_group = classify_directness(directness),
    direction_clean = factor(direction_clean, levels = c("Supportive", "Null/mixed", "Opposite")),
    study_label = paste0(first_author_year, " (n = ", ifelse(is.na(sample_size), "NR", sample_size), ")")
  ) |>
  dplyr::arrange(analysis_domain, first_author_year) |>
  dplyr::mutate(study_label = factor(study_label, levels = rev(unique(study_label))))

fig_harvest_main <- ggplot2::ggplot(harvest_data_main, ggplot2::aes(x = manuscript_section_axis, y = study_label)) +
  ggplot2::geom_point(
    ggplot2::aes(size = sample_size_sqrt, shape = directness_group, fill = direction_clean),
    color = "black", alpha = 0.92, stroke = 0.45
  ) +
  ggplot2::scale_fill_manual(
    values = direction_cols,
    name = "Direction of evidence",
    labels = c(
      "Supportive" = "Supportive: finding matches the prespecified hypothesis",
      "Null/mixed" = "Null/mixed: no clear or inconsistent directional support",
      "Opposite" = "Opposite: finding goes against the hypothesis"
    ),
    drop = FALSE
  ) +
  ggplot2::scale_size_continuous(
    range = c(2.8, 7.4),
    guide = "none"
  ) +
  ggplot2::scale_shape_manual(
    values = c("Direct/partly direct" = 21, "Indirect/mechanistic" = 22),
    name = "Evidence directness",
    labels = c(
      "Direct/partly direct" = "Direct/partly direct",
      "Indirect/mechanistic" = "Indirect/mechanistic"
    ),
    drop = FALSE
  ) +
  ggplot2::labs(
    title = "Diet–microbiome–ARG evidence by manuscript section",
    x = NULL,
    y = "Citation and sample size"
  ) +
  ggplot2::guides(
    fill = ggplot2::guide_legend(
      override.aes = list(shape = 21, size = 5, colour = "black", alpha = 1),
      order = 1
    ),
    shape = ggplot2::guide_legend(
      override.aes = list(fill = "grey85", size = 5, colour = "black", alpha = 1),
      order = 2
    ),
    size = "none"
  ) +
  article_theme +
  ggplot2::theme(
    axis.text.x = ggplot2::element_text(size = 8.4, face = "bold", angle = 45, hjust = 1, vjust = 1, lineheight = 0.90),
    axis.text.y = ggplot2::element_text(size = 8.2),
    plot.title = ggplot2::element_text(size = 13.0, face = "bold", margin = ggplot2::margin(b = 4)),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.text = ggplot2::element_text(size = 7.6),
    legend.title = ggplot2::element_text(size = 8.2, face = "bold"),
    plot.margin = ggplot2::margin(5.5, 7, 5.5, 5.5)
  )

fig_harvest_main
fig_manifest_harvest_main <- save_article_plot(fig_harvest_main, "MAIN_FIGURE_03_harvest_plot_diet_microbiome_ARG_evidence", width = 8.27, height = 6.9, main = TRUE)
```

## Main Figure 4. A4 combined panel: Bayesian direction synthesis + harvest plot

```{r main-figure-combined-a4-panel, fig.height=11.69}
# A4 portrait panel: better for manuscript review PDFs. The Bayesian panel includes the
# secondary descriptive combined-domain posterior, while the harvest panel remains
# organized by the three manuscript sections.
fig_bayes_panel <- fig_bayes_main +
  ggplot2::labs(tag = "A") +
  ggplot2::theme(
    plot.title = ggplot2::element_text(size = 13.0, face = "bold"),
    strip.text = ggplot2::element_text(size = 7.8, face = "bold", lineheight = 0.88),
    axis.title = ggplot2::element_text(size = 9.2),
    axis.text = ggplot2::element_text(size = 8.0)
  )

fig_harvest_panel <- fig_harvest_main +
  ggplot2::labs(tag = "B") +
  ggplot2::theme(
    plot.title = ggplot2::element_text(size = 13.0, face = "bold"),
    axis.title = ggplot2::element_text(size = 9.2),
    axis.text.x = ggplot2::element_text(size = 7.4, angle = 45, hjust = 1, vjust = 1, lineheight = 0.90),
    axis.text.y = ggplot2::element_text(size = 8.1),
    legend.text = ggplot2::element_text(size = 7.4),
    legend.title = ggplot2::element_text(size = 8.2, face = "bold"),
    legend.key.height = grid::unit(0.18, "in")
  )

# NOTE: We avoid patchwork's `& theme(...)` operator here because recent
# ggplot2/S7 + patchwork combinations can throw:
# "Can't find method for generic `&(e1, e2)`: e1: <patchwork>; e2: <theme>".
# The legend placement is therefore applied directly to the individual panels
# above and to the patchwork annotation theme below.
combined_panel_portrait <- fig_bayes_panel / fig_harvest_panel +
  patchwork::plot_layout(heights = c(0.48, 0.52), guides = "collect") +
  patchwork::plot_annotation(
    title = "Quantitative synthesis of diet–microbiome–ARG evidence",
    theme = ggplot2::theme(
      plot.title = ggplot2::element_text(face = "bold", size = 14),
      plot.margin = ggplot2::margin(6, 6, 6, 6),
      legend.position = "bottom"
    )
  )

combined_panel_portrait
fig_manifest_combined_portrait <- save_article_plot(
  combined_panel_portrait,
  "MAIN_FIGURE_04_A4_PORTRAIT_combined_bayesian_harvest_panel",
  width = 8.27, height = 11.69, main = TRUE
)

# A4 landscape version: often easier to insert into slides or broad journal layouts.
combined_panel_landscape <- fig_bayes_panel / fig_harvest_panel +
  patchwork::plot_layout(heights = c(0.38, 0.62), guides = "collect") +
  patchwork::plot_annotation(
    title = "Quantitative synthesis of diet–microbiome–ARG evidence",
    theme = ggplot2::theme(
      plot.title = ggplot2::element_text(face = "bold", size = 14),
      plot.margin = ggplot2::margin(6, 6, 6, 6),
      legend.position = "bottom"
    )
  )

fig_manifest_combined_landscape <- save_article_plot(
  combined_panel_landscape,
  "MAIN_FIGURE_04_A4_LANDSCAPE_combined_bayesian_harvest_panel",
  width = 11.69, height = 8.27, main = TRUE
)
```

## Supplement Figure. Descriptive effect-size anchors, no pooling

```{r supp-figure-descriptive-effects, fig.height=7}
forest_data <- effect_table |>
  dplyr::filter(!is.na(log_effect)) |>
  dplyr::mutate(
    label = paste0(first_author_year, " | ", outcome),
    label = forcats::fct_reorder(label, log_effect),
    uncertainty_label = dplyr::if_else(has_uncertainty, "With uncertainty", "No uncertainty"),
    ci_log_lower_plot = dplyr::if_else(has_uncertainty, ci_log_lower, log_effect),
    ci_log_upper_plot = dplyr::if_else(has_uncertainty, ci_log_upper, log_effect),
    ratio_label = dplyr::case_when(
      has_uncertainty ~ paste0("Ratio = ", fmt2(effect_exp), " [", fmt2(ci_exp_lower), ", ", fmt2(ci_exp_upper), "]"),
      TRUE ~ paste0("Ratio = ", fmt2(effect_exp), " (no CI)")
    )
  )

if (nrow(forest_data) > 0) {
  x_min <- min(forest_data$ci_log_lower_plot, na.rm = TRUE) - 0.30
  x_max <- max(forest_data$ci_log_upper_plot, na.rm = TRUE) + 0.75
  fig_forest <- ggplot2::ggplot(forest_data, ggplot2::aes(y = label, x = log_effect)) +
    ggplot2::geom_vline(xintercept = 0, linetype = "dashed", color = "grey40") +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_log_lower_plot, xmax = ci_log_upper_plot), height = 0.18, linewidth = 0.7) +
    ggplot2::geom_point(ggplot2::aes(shape = uncertainty_label), size = 3.8) +
    ggplot2::geom_text(ggplot2::aes(label = ratio_label), nudge_x = 0.22, hjust = 0, size = 3.0) +
    ggplot2::facet_wrap(~ analysis_domain, scales = "free_y", ncol = 1) +
    ggplot2::coord_cartesian(xlim = c(x_min, x_max), clip = "off") +
    ggplot2::labs(
      title = "Extractable quantitative anchors, displayed descriptively",
      subtitle = "Positive log effects indicate higher ARG outcome in the higher-risk exposure. Effects use different metrics and are not pooled.",
      x = "Log effect size",
      y = NULL,
      shape = "Uncertainty"
    ) +
    article_theme +
    ggplot2::theme(plot.margin = ggplot2::margin(10, 100, 10, 16))
  fig_forest
  fig_manifest_forest <- save_article_plot(fig_forest, "SUPP_FIGURE_descriptive_effect_size_forest_no_pooling", width = 13, height = 8, main = FALSE)
} else {
  fig_manifest_forest <- tibble::tibble(figure = "SUPP_FIGURE_descriptive_effect_size_forest_no_pooling", set = "Supplement", png = NA_character_, tiff = NA_character_, pdf = NA_character_, dpi = DPI_EXPORT, width_in = NA_real_, height_in = NA_real_)
  cat("No log-effect rows available for descriptive effect-size plot.\n")
}
```

## Supplement Figure. Evidence heatmap audit trail

```{r supp-figure-heatmap, fig.height=8}
heatmap_data <- study_sign |>
  dplyr::mutate(
    study_label = paste0(first_author_year, " (", study_id, ")"),
    study_label = forcats::fct_rev(forcats::fct_inorder(study_label)),
    directness_code = make_directness_code(directness)
  )

fig_heatmap <- ggplot2::ggplot(heatmap_data, ggplot2::aes(x = analysis_domain, y = study_label, fill = direction_clean)) +
  ggplot2::geom_tile(color = "white", linewidth = 0.7) +
  ggplot2::geom_text(ggplot2::aes(label = directness_code), size = 3.0) +
  ggplot2::scale_fill_manual(values = direction_cols, drop = FALSE) +
  ggplot2::labs(
    title = "Evidence heatmap by study and synthesis domain",
    subtitle = "Tile fill shows direction; cell code shows directness (D = direct, I = indirect, M = mechanistic).",
    x = NULL,
    y = NULL,
    fill = "Direction"
  ) +
  article_theme +
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 25, hjust = 1))

fig_heatmap
fig_manifest_heatmap <- save_article_plot(fig_heatmap, "SUPP_FIGURE_study_domain_evidence_heatmap", width = 12, height = 9, main = FALSE)
```

## Supplement Figure. Meta-analysis readiness traffic-light plot

```{r supp-figure-meta-readiness, fig.height=5}
readiness_plot_data <- meta_readiness |>
  dplyr::mutate(
    label = paste0(as.character(analysis_domain), "\n", effect_metric, " | ", outcome),
    label = short_wrap(label, 45),
    label = forcats::fct_reorder(label, unique_studies)
  )

fig_readiness <- ggplot2::ggplot(readiness_plot_data, ggplot2::aes(x = unique_studies, y = label, fill = readiness)) +
  ggplot2::geom_col(width = 0.65, color = "white") +
  ggplot2::geom_text(ggplot2::aes(label = paste0("n=", unique_studies, "; CI rows=", rows_with_uncertainty)),
                     hjust = -0.05, size = 3.0) +
  ggplot2::scale_fill_manual(values = traffic_cols, drop = FALSE) +
  ggplot2::scale_x_continuous(expand = ggplot2::expansion(mult = c(0, 0.25))) +
  ggplot2::labs(
    title = "Meta-analysis readiness check",
    subtitle = "Random-effects pooling was not run because no domain had ≥3 comparable estimates with uncertainty.",
    x = "Unique studies contributing to comparable effect-size group",
    y = NULL,
    fill = "Readiness"
  ) +
  article_theme

fig_readiness
fig_manifest_readiness <- save_article_plot(fig_readiness, "SUPP_FIGURE_meta_analysis_readiness", width = 11, height = 6, main = FALSE)
```

# 10. Export final article tables, figures and workbook

```{r final-export}
figure_manifest <- dplyr::bind_rows(
  fig_manifest_bayes_main,
  fig_manifest_pathway_main,
  fig_manifest_harvest_main,
  fig_manifest_combined_portrait,
  fig_manifest_combined_landscape,
  fig_manifest_strength,
  fig_manifest_direction_comp,
  fig_manifest_forest,
  fig_manifest_heatmap,
  fig_manifest_readiness
)
write_csv_table(figure_manifest, "figure_manifest_png_tiff_pdf_1000dpi.csv")

# Main and supplementary table exports.
main_table_list <- list(
  MAIN_Table_1_Direction_Bayes = main_results_table,
  MAIN_Decision_Log = decision_log
)

supp_table_list <- list(
  S_Table_Study_Extraction = study_table,
  S_Table_Meta_Readiness = meta_readiness,
  S_Table_Primary_Direction = study_direction_final,
  S_Table_Outcome_Sensitivity = outcome_sensitivity,
  S_Table_RoB_Directness = rob_summary,
  S_Table_Restricted_Sensitivity = primary_restricted,
  S_Table_Effect_Anchors = effect_table,
  S_Table_Pathway_Evidence = pathways,
  S_Table_Figure_Manifest = figure_manifest,
  S_Table_Article_Results = article_results
)

final_xlsx <- file.path(out_dir, "diet_ARG_FINAL_IMPROVED_article_quantitative_outputs.xlsx")
openxlsx::write.xlsx(c(main_table_list, supp_table_list), file = final_xlsx, overwrite = TRUE)

cat("\nFinal processed XLSX written to:\n", final_xlsx, "\n")
cat("\nTables written to:\n", table_dir, "\n")
cat("\nMain figures written to:\n", main_figure_dir, "\n")
cat("\nSupplementary figures written to:\n", supp_figure_dir, "\n")
```

```{r session-info}
sessionInfo()
```
